\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage[left=1.00in, right=1.00in, top=1.00in, bottom=1.00in]{geometry}
\title{CS348 Project Milestone 0}
\author{Keshav Gupta\and Isshana Mohanakumar \and Edward Pei \and Ricky Lu \and Govind Nair}
\begin{document}
\maketitle

\section*{Our Application}
Our group is creating a web application that will allow users to manage, rate, and analyse movies registered in the IMDB database. We will also include trivia features so that users can test themselves on how well they know the film industry. Our target demographic is people who are obsessed with finding and keeping track of their film catalogue. Our users are the kind of people who want to know everything about the industry and become critics.\\\\We will use the \href{https://datasets.imdbws.com/}{IMDB dataset} to download the Movie and Actor/Actress catalogues. 

\section*{Platform and Tech Stack}
Our front-end interface will be a web application built in React. Our back-end API server will be built with Node.js and Express.js. These will rely on a MySQL database. Generally, our entire tech stack will be built with either JavaScript or TypeScript with SQL queries to interact with the database. We also expect to use some Python to process CSV files from the \href{https://datasets.imdbws.com/}{IMDB dataset} into our MySQL database.\\\\All of this will need to be run locally and requires \href{https://nodejs.org/en/download}{Node v18.5.0}, \href{https://nodejs.org/en/download}{NPM v8.12.1}, \href{https://dev.mysql.com/downloads/mysql/}{MySQL v8.0.33}. The application may work for other versions, but we will be developing and testing it using the ones specified above.

\section*{Members}
\begin{itemize}
    \item \textbf{Keshav Gupta} created the initial GitHub repository and scripts to show how to connect and use the database. Brainstormed project features, and tech stack.
    \item \textbf{Isshana Mohanakumar} contributed to writing the M0 report. Brainstormed project features, and tech stack.
    \item \textbf{Edward Pei} contributed to writing the M0 report. Brainstormed project features, and tech stack.
    \item \textbf{Ricky Lu} contributed to writing the M0 report. Brainstormed project features, and tech stack.
    \item \textbf{Govind Nair} contributed to writing the M0 report. Brainstormed project features, and tech stack.

\end{itemize}
\section*{GitHub}

All code is available in GitHub repository: \href{https://github.com/Kggupta/FilmFlix}{FilmFlix}
\\\\See the \textbf{README.md} file for "Hello World" database startup guide.

\end{document}